Community-Conditioned Language Models

### 2020-11-02 paper/paper.tex
tweaks

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{pgfplots}
\usepackage{todonotes}
\renewcommand{\UrlFont}{\ttfamily\small}
\usepgfplotslibrary{groupplots}
\pgfplotsset{compat=1.17}

@@

Reddit is divided into forums called \textit{subreddits}, 
which are typically organized around a topic of interest. 
Our dataset includes comments from \num{46} subreddits, 
randomly selected from the set of all forums 
with at least \num{15000} comments per month for each month 
in the three years between 2015 and 2017.\footnote{
We initially selected \num{50} subreddits, 
but excluded four from further analysis: 
two which were primarily non-English and two with particularly short average comment lengths.}
Each community corpus consist of \num{50000} randomly selected comments from the year 2015.

Comments were preprocessed as follows: 
We removed markdown formatting, extracting only rendered text. 
We exclude the content of block quotes, code blocks, and tables. 
We tokenized the comments using the default English model for the SpaCy tokenizer,\footnote{Version 2.2.3}
and lower-cased all tokens.

@@

We combined the 46 community corproa and split the combined corpus,
reserving 10\% for testing, 10\% for validation and the rest for training.
Splits were stratified by community so that the same number of training examples
were available for each community.

@@

As a qualitative assesment of the community embeddings, 
we identified several topic categories into which at least three
of the selected communities fall. 
We plotted the two-component PCA projection of the embeddings,
annotated with these topic categories.
We see that there is some evidence of clustering according to
the topic categories we identified,
suggesting that the embedding space learned by the model is meaningful.

\begin{figure*}
\begin{tikzpicture}
  \commpcagroupplot{floats/lstm-3-1_pca.csv}{floats/transformer-3-3_pca.csv}
\end{tikzpicture}
\caption{Community embedding PCA of the best LSTM (left, $c=1$) and transformer (right, $c=3$) models.}
\label{fig:lstm-pca}
\end{figure*}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{pgfplots}
\usepackage{todonotes}
\renewcommand{\UrlFont}{\ttfamily\small}
\usepgfplotslibrary{groupplots}
\pgfplotsset{compat=1.16}

@@

Reddit is divided into forums called \textit{subreddits}, 
which are typically organized around a topic of interest. 
Our dataset includes \emph{comments}\jp{Comments/Post terminology; make sure its consistens} from \num{46} subreddits, 
randomly selected from the set of all forums 
with at least \num{15000} comments per month for each month
in the three years between 2015 and 2017. 
We initially selected \num{50} subreddits, 
but excluded four of them from further analysis: 
two which were primarily non-English and two with particularly\jp{quantify?} short average comment lengths.
Each community corpus consist of \num{50000} randomly selected comments from the year 2015.

Comments were preprocessed as follows: 
We excluded the content of block quotes, code blocks, and tables.
We removed any markup (formatting) commands from the remaining text, extracting only rendered text.
We tokenized the comments using the default English model for the SpaCy tokenizer Version 2.2.3\jp{citation?}
and lower-cased all tokens.

@@

We combined the 46 community corpora and split the combined corpus\jp{unclear if there is balancing between },
reserving 10\% for testing, 10\% for validation and the rest for training.
Splits were stratified by community so that the same number of training examples
were available for each community.

@@

As a qualitative assesment of the community embeddings, 
we identified several topic categories into which at least three
of the selected communities fall. 
We plotted the two-component PCA projection of the embeddings,
annotated with these topic categories (Figure~\ref{comm-pca}).
We see that there is some evidence of clustering according to
the topic categories we identified,
suggesting that the embedding space learned by the model is meaningful.

\begin{figure*}
\begin{tikzpicture}
  \commpcagroupplot{floats/lstm-3-1_pca.csv}{floats/transformer-3-3_pca.csv}
\end{tikzpicture}
\caption{Community embedding PCA of the best LSTM (left, $c=1$) and transformer (right, $c=3$) models.}
\label{fig:comm-pca}
\end{figure*}
